An OSGi-based Sensor Network for \\ Environmental Monitoring

### 2009-03-03 docs/icccn2009/paper.tex
Paste more text
git-svn-id: svn://localhost/netbeams/trunk@328 559edde2-a4d4-44e0-96fc-4035e40d7396

\section{Use Case}

@@

@@

Should explain some specific DC and DP we have implemented for
NetBEAMS. Length: 1 - 1.5 pages.

@@

>>>>

\section{Requirement Analysis}

@@

Micro-kernel architecture.

@@

In the following we present a practical application the the DSP
presented in the previous section. We describe a deployment of the DSP
using sensor owned and operated by the RTC. Our environmental sensor
network is dubbed NetBEAMS (Networked Bay Environmental Assessment
Monitoring System) and allows access to sensor equipment deployed
throughout the San Francisco Bay Area. Figure \ref{FIG_NETBEAMS}
provides an end-to-end overview of the NetBEAMS architecture. NetBEAMS
is built using multiple installtion of the DSP. One DSP installation
is collocated with each sensor and an additional DSP is running on the
backend server.

@@

To describe NetBEAMS is to describe the specific DC and DP we have
implemented. On the far left of Figure \ref{FIG_NETBEAMS} is the
actual sensor; in our case the aforementioned Seabird sensor.
Collocated with the Seabird is an embedded system. Here we make use of
a platform called Gumstix.

The Gumstix is a single-board computers with 256 Mb of flash and 256
Mb of SDRAM, and running a 600 MHz TI OMAP 3503 processor. Additional
features can be added to the motherboard with expansion cards
connected via on-board buses. The motherboards draw less than 250 mA
@4V at 400 MHz and less than 50 mA while idling, waiting for input.
Gumstix run Linux 2.6 with the BusyBox utilities, and use the
OpenEmbedded build environment to provide a complete Linux
environment and a large range of Linux applications. We use the JamVM
implementation of Sun Microsystem's virtual machine to execute Java
programs.

Cellular communication platform.
